Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-20 scripts/MouseSexDiffApril20_2020.Rmd
Extraction of I2 during secondary meta analysis

      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), means$k)
      results_alltraits_grouping[t, 15] <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}
```

@@

```{r}
Behaviour <- overall1 %>% 
  filter(., GroupingTerm == "Behaviour") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Immunology <- overall1 %>% 
  filter(., GroupingTerm == "Immunology") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Hematology <- overall1 %>% 
  filter(., GroupingTerm == "Hematology") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Hearing <- overall1 %>% 
  filter(., GroupingTerm == "Hearing") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Physiology <- overall1 %>% 
  filter(., GroupingTerm == "Physiology") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Metabolism <- overall1 %>% 
  filter(., GroupingTerm == "Metabolism") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Morphology <- overall1 %>% 
  filter(., GroupingTerm == "Morphology") %>%
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Heart <- overall1 %>% 
  filter(., GroupingTerm == "Heart") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_se)

Eye <- overall1 %>% 
  filter(., GroupingTerm == "Eye") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
  )  %>%
    select(., GroupingTerm, lnCVR:lnRR_se)

All <- overall_all1 %>% 
  mutate(
    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, 
    lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,
    lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se
  )  %>%
    select(., lnCVR:lnRR_se)

@@

```{r}
#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity

@@

This figure is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison. The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance). Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
```{r}
library(ggpubr)
FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1, 1)
)

>>>>

      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), means$k)
      results_alltraits_grouping[t, 15] <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}

@@

```{r}
Behaviour <- overall1 %>% 
  filter(., GroupingTerm == "Behaviour") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Immunology <- overall1 %>% 
  filter(., GroupingTerm == "Immunology") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Hematology <- overall1 %>% 
  filter(., GroupingTerm == "Hematology") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Hearing <- overall1 %>% 
  filter(., GroupingTerm == "Hearing") %>% 
  mutate(
    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Physiology <- overall1 %>% 
  filter(., GroupingTerm == "Physiology") %>% 
  mutate(
   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,  lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Metabolism <- overall1 %>% 
  filter(., GroupingTerm == "Metabolism") %>% 
  mutate(
  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Morphology <- overall1 %>% 
  filter(., GroupingTerm == "Morphology") %>%
  mutate(
   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Heart <- overall1 %>% 
  filter(., GroupingTerm == "Heart") %>% 
    mutate(
   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

Eye <- overall1 %>% 
  filter(., GroupingTerm == "Eye") %>% 
  mutate(
 lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
  )  %>%
  select(., GroupingTerm, lnCVR:lnRR_I2)

All <- overall_all1 %>% 
  mutate(
    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se,     lnCVR_I2 = .[[2]][[1]]$I2,
    lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,     lnVR_I2 = .[[3]][[1]]$I2,
    lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se, lnRR_I2 = .[[4]][[1]]$I2,
  )  %>%
    select(., lnCVR:lnRR_I2)

@@

```{r FigS1, fig.height = 8, fig.width = 7}
#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity

@@

This figure is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison. The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance). Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
```{r FigS2, fig.height = 8, fig.width = 7}
library(ggpubr)
FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1, 1)
)
